Constant Partying: \\ Introducing a Generic Toolkit for Recursive Partitioning in R

### 2014-03-18 pkg/partykit/inst/NUS-2014/constparty.Rnw
improved M&S example
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@501 255f4249-2263-4417-b1ea-8498779e27a7

<<ms63-party, echo=TRUE, results=verbatim>>=
ms63d
pn <- partynode(1L,
  split = partysplit(2L, index = 1:2),
  kids = list(
    partynode(2L, info = "$5500"),
    partynode(3L, info = "$3000")
  )
)
py <- party(pn, ms63d)
print(py)
plot(py)
@

@@

\setkeys{Gin}{width=1.2\textwidth}
\hspace*{-1cm}%
<<ms63-plot2, fig=TRUE, height=8, width=14>>=
plot(ms63p, drop = TRUE)
@

>>>>

<<ms63-party, echo=TRUE, results=verbatim>>=
str(ms63d)
pn <- partynode(1L,
  split = partysplit(2L, index = 1:2),
  kids = list(
    partynode(2L, info = "$5500"),
    partynode(3L, info = "$3000")
  )
)
py <- party(pn, ms63d)
print(py)
plot(py)
@

@@

\setkeys{Gin}{width=1.2\textwidth}
\hspace*{-1cm}%
<<ms63-plot2, fig=TRUE, height=8, width=14>>=
plot(ms63p, drop = TRUE, ep_args = list(justmin = 10))
@
